Reproducible psychological research and project management in R

### 2019-10-09 slides/vertical_intro.Rmd
first commit

>>>>

# R markdown (.Rmd files)

A text file for **notes and R scripts** that compiles to different formats (html, pdf, etc.)

```{r}
knitr::include_graphics("imgs/rmarkdown.png")
```

# Data frames

```{r, echo=TRUE}
all_data <- data.frame(trial = 1:6,
                       congruency = rep(c("con","inc"), each = 3),
                       rt = rnorm(6, mean = 0, sd = 100),
                       accuracy = c(1,1,1,1,0,1))
all_data
```

# dplyr - tidyverse Data Wrangling

```{r, echo=T}
library(tidyverse)
df <- all_data %>%
  filter(accuracy == 1) %>%
  group_by(congruency) %>%
  summarise(mean_rt = mean(rt))
```

# ggplot2 - tidyverse plotting

```{r, echo=TRUE, fig.height=3}
ggplot(df, aes(x=congruency, y=mean_rt))+
  geom_bar(stat="identity", position="dodge") +
  theme_classic()
```
